Universal Anonymous Signatures

### 2022-07-28 prism-backend/research/gsac/app-related-extra.tex
Moved RAC to main body, and DAC to app. Sync'ed RAC with new syntax.

\subsection{Revocable Anonymous Credentials}
\label{sapp:related-models-rac}

In \cite{cks10}, revocable anonymous credentials are proposed. From \CUASGen, it
is straightforward to build an AC system with verifier local revocation, like in
\cite{bs04}. Basically, all credentials get an identifier as first attribute,
and \feval functions prove that the opener can retrieve that identifier. Then,
in case of needing to revoke a concrete credential, any verifier can interact
with the opener to add an identifier to its own revocation list (alternatively,
there can be a public list of revoked credentials). Having \feval functions
prove that the credential identifier does not belong to that list thus directly
implements privacy-preserving revocation. We first give a simple model in
\figref{fig:model-rac}, extending that in \appref{sapp:related-models-ac}. As
before, for simplicity we assume only one credential is used per authentication
(the extension being direct). To the functionality in
\appref{sapp:related-models-ac}, we now explicitly add the $OKeyGen$ function
(equivalent to \OKeyGen, with a fixed \finsp function),
which generates the opener key pair, extend $Verify$ to receive also a list $L$
of revoked identifiers, and we add a function (and corresponding oracle) $id/\bot
\gets RetrieveCredId(\osk,\utrans)$ that can extract the identifier of the
credential used in a presentation transcript \utrans -- and which is essentially
equivalent to \Open in \UAS. For simplicity, we do not include the equivalent to
verifiable openings, but this would be straightforward.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.45\textwidth}
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\opk,\osk) \gets \OKeyGen(\parm) \\        
        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
        b^* \gets \adv^{\mathcal{O}_{anon}}(\parm,\ipk,\opk) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.55\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (\opk,\osk) \gets \OKeyGen(\parm) \\        
        (\ipk,\isk) \gets IssKeyGen(\parm) \\
        (D,L,\st) \gets
        \adv^{\mathcal{O}_{forge}}(\parm,\ipk) \\
        \langle \cdot,(b,\utrans)\rangle
        \gets \langle \adv(\st),\Verify(\ipk,D,L)\rangle \\
        \pcif b = 0: \pcreturn 0 \\
        \pcif \nexists j~\suchthat~(\OWNR[j] \in \CU
        \land D \subseteq \ATTR[j]): \pcreturn 1 \\    
        h \gets RetrieveCredHandle(\osk,\utrans) \\
        \pcif h \in L \lor h = \bot: \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for revocable anonymous credentials with selective
    disclosure based on \cite{fhs19}. 
    $\mathcal{O}_{anon} \gets \lbrace HU,CU,Obtain,Issue,ObtIss,Show,
    ReqCredHandle,LoR\rbrace$. $\mathcal{O}_{forge} \gets \lbrace HU,CU,
    Obtain,ObtIss,Issue,Show,ReqCredHandle \rbrace$. $ReqCredHandle$ is
    equivalent to \OPEN, operating on transcripts \utrans instead of signatures.
    Also, \OWNR and \ATTR tables are essentially as in \secref{ssec:model-uas}.}
  \label{fig:model-rac}  
\end{figure}

\subsubsection{\CUASRAC Construction.} %

For our RAC construction, we define signature evaluation and opening functions
as follows:

\begin{align}
  & \feval^{\dattrs,F,V,L}(\usk,\cred,\msg) \coloneqq
    \lbrace
    \pcif F(V,\attrs_1(\cred)) \in L: \pcreturn (0,0);
    \pcelse \pcreturn (\dattrs(\cred),V)
    \rbrace \nonumber \\
  & \finsp^{F}((\yeval^0,\yeval^1),\usk,\cred,\msg) \coloneqq
    \lbrace
    \pcif \yeval^0 \neq 0: \pcreturn F(\yeval^1,\attrs_1(\cred));
    \pcelse \pcreturn 0
     \rbrace
  \label{eq:funcs-rac}
\end{align}

Where, $\feval^{\dattrs,F,V,L}$ is parameterized with a one-way and
collision-resistant function $F$
(e.g., a cryptographic hash), some constant subset \dattrs of attributes to be
selectively disclosed by signers, a string identifying the verifier $V$ and a
list $L$ of ``revocation handles'' by this verifier. If the credential used for
signing has been revoked (i.e., if $F(V,id) \in L$), then \feval returns $0$, as
an indication that the signature should be rejected by the verifier. Otherwise,
it sets $\yeval^0 \gets \dattrs(\cred)$, and $\yeval^1 \gets V$ -- note that
$\yeval^1$ will be encrypted with a single-use key pair.
%
On the other hand, $\finsp^{F}$ outputs $F(\yeval^1,\attrs_1(\cred))$, allowing
valid signatures to be locally revocable by $V$ at a later stage, since
$\yeval^1=V$.

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\Setup(1^\secpar)$ as in
  \CUASGen.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \IKeyGen from our
  \CUASGen construction, setting $\fissue^1$ as issuance function.
\item[$(\ipk,\isk) \gets OKeyGen(\parm)$.] Runs \OKeyGen from our
  \CUASGen construction, setting $\finsp^F$ as opening function.
\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \UKeyGen from the
  \CUASGen construction, and computes $\CCommit(\usk;0)$ as \upk.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
  $\fissue^1$ as issuance function.
\item[$\langle 1/0,(1,\utrans)/(0,\utrans)\rangle \gets \langle Show(\ipk,\attrs,\dattrs,\cred),
  \Verify(\ipk,\dattrs) \rangle$.]
  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
  using $\feval^{\dattrs,F,V,L}$ as signature evaluation function, and
  $\finsp^F$ as open function.
\item[$h/\bot \gets RetrieveCredHandle(\osk,\utrans)$.]
  Outputs the revocation handle $h$ for the credential used in the interactive
  presentation associated to \utrans. Note that $h$ is verifier-dependent.
\end{description}

\paragraph{Security of \CUASRAC.} %
We prove that \CUASRAC is an anonymous and unforgeable anonymous credential
scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
is anonymous and has unforgeable signing. Note that issuance unforgeability
of \CUASGen is not needed, as the model in \cite{fhs19} does not allow
leveraging other credentials not any fixed custom issuance policy. Thus,
signature unforgeability from \UAS is enough. Note that AC schemes modelled
as in \cite{fhs19} do not have issuance anonymity, as the user public key
is passed to the issuer.

\begin{theorem}[Anonymity of \CUASRAC]
  \label{thm:anon-cuasac}
  If the base \CUASGen construction has signature anonymity according to
  \defref{def:sign-anonymity-uas}, and $F$ is one-way and collision-resistant,
  then \CUASAC is an anonymous AC scheme according to \cite{fhs19}.
\end{theorem}

\begin{proof}
  Given \adv~ against anonymity of \CUASRAC as defined in
  \figref{fig:model-rac}, we build an adversary \advB against anonymity of
  \CUASGen as defined in \defref{def:sign-anonymity-uas}.

  First observe that, given a revocation handle $F(V,id)$ extracted from any
  credential showing, it is not possible to extract $id$, as $F$ is one-way
  and collision-resistant.

  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
  oracle, i.e.: for calls to $HU,CU,Obtain,Show,LoR,ReqCredHandle$, \advB
  redirects to \HUGEN, \CUGEN, \OBTAIN, \SIGN, \CHALb, of \OPEN respectively.
  Note that ``translating'' the inputs from the former into inputs for the
  latter is trivial. Also, observe that $ReqCredHandle$ essentially refuses to
  open transcripts from challenge users (signatures, in the non-interactive
  equivalent), as $F(V,\attrs_1(\ccid_0) \neq F(V,\attrs_1(\ccid_1)$ with
  overwhelming probability (see the $\tyinsp \neq \yinsp$) check in
  \figref{fig:oracles2}. Obviously, if \adv~ wins in its anonymity game, then
  so does \advB with the same probability.
  % 
  \qed
\end{proof}

\begin{theorem}[Unforgeability of \CUASRAC]
  If the base \CUASGen construction has sign unforgeability according to
  \defref{def:sign-forge-uas}, and $F$ is one-way and collision-resistant, then
  \CUASRAC is an unforgeable RAC scheme.
\end{theorem}

\begin{proof}
  Given \adv~ against unforgeability of \CUASRAC as defined in
  \figref{fig:model-rac}, we build an adversary \advB against sign
  unforgeability of \CUASGen as defined in \defref{def:sign-forge-uas}.

  To simulate oracle calls by \adv, \advB acts as in the anonymity proof. Assume
  that \adv~ wins its game via the winning condition of line 6 in the RAC
  unforgeability game. The same reasoning as in \CUASAC applies here. Next, note
  that the probability of \adv~ winning its game via the winning condition at
  line 9 is negligible, due to soundness of the NIZK scheme used for signing,
  and the one-wayness and collision-resistance of $F$ in
  $\feval^{\dattrs,F,V,L}$ and $\finsp^{F}$.
  % 
  \qed
\end{proof}

>>>>

\subsection{Delegatable Anonymous Credentials}
\label{ssec:related-models-dac}

We give a simple definition for a Delegatable Anonymous Credentials (DAC)
scheme, extending \cite{fhs19} and inspired by \cite{bcc+09}. Unlike the latter,
our simple scheme built from $\CUASGen^{usr-iss}$ does not ensure privacy of the
delegation chain -- which could be achieved by making \feval output projective
proofs like in \cite{bcc+09}, but since our goal is to showcase the feasibility
of building DAC from \UAS, we leave that out for brevity. Our simple scheme
does, however, ensure that a (not top-level) issuer can only delegate attributes
contained in a credential it owns. Also, for simplicity, we restrict to the case
of using one credential per signature/interactive credential presentation, and
assume that all parties use the same opener and \finsp function.
%
The functionality is thus defined almost as in \secref{ssec:related-models-ac},
i.e., we have $Setup$, $IssKeyGen$ algorithms, and $\langle Obtain,Issue\rangle$
and $\langle Show,Verify \rangle$ interactive protocols; but we do not have
$UserKeyGen$, as this collapses with $IssKeyGen$.
%
In the model for this setting, since there are multiple issuers, in addition
to the oracles in \secref{ssec:related-models-ac}, we use $HI$ and $CI$ oracles,
equivalent to \IGEN and \ICORR in our \UAS model, which allow adding honest
issuers, and corrupt existing ones, respectively. The issuance and sign
anonymity properties are direct, constraining the adversary to output challenge
credentials and signatures with the same delegation chain. For unforgeability,
we still require that no adversary can authenticate using a set of attributes
that have not been issued to a corrupt user. In addition, we require that for
any successful authentication using a level-$l$ credential, we
can extract a chain of credentials of length $l$ such that each level-$i$
credential can be used successfully to authenticate a level-$(i+1)$ credential
down to the level-$l$ credential, and the attributes revealed in the
level-$l$ authentication are contained in all the credentials up the chain.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.45\textwidth}
      \procedure[linenumbering]{$\Exp^{iss-anon-b}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        b^* \gets \adv^{\mathcal{O}_{iss-anon}}(\parm) \\
        \pccomment{Abort if challenge creds belong to} \\
        \pccomment{users with different delegation chains} \\
        \pcreturn b^*
      }
      \vspace*{0.5em}

      \procedure[linenumbering]{$\Exp^{sig-anon-b}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        b^* \gets \adv^{\mathcal{O}_{sig-anon}}(\parm) \\
        \pccomment{Abort if challenge sigs belong to} \\
        \pccomment{users with different delegation chains} \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.55\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,dac}(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        (D=(l,D'),\ipk_l,\st) \gets
        \adv^{\mathcal{O}_{forge}}(\parm) \\
        \langle\cdot,(b,\utrans)\rangle \gets
        \langle \adv(\st),\Verify(\ipk_l,D)\rangle \\
        \pcif b = 0: \pcreturn 0 \\
        \pcif \nexists j~\suchthat~(\OWNR[j] \in \CU
        \land D \subseteq \ATTR[j]): \pcreturn 1 \\        
        (ipk_0, \lbrace (\ipk_i,\cred_i) \rbrace_{i \in [1,l]})
        \gets ExtractChain(\utrans) \\ 
        \pcif \exists i \in [1,l]~\suchthat~
        \iid = \ISR[\ipk_{i-1}] \notin \CI~\land \\
        \pcind D' \not\subseteq \ATTR[\iid]) \land
        D' \subseteq \ATTR[\ISR[\ipk_i]]: \\
        \pcind \pcreturn 1 \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for delegatable anonymous credentials with selective
    disclosure based on \cite{fhs19}. $\mathcal{O}_{iss-anon} \gets \lbrace HI,
    CI,Obtain,Issue,ObtIss,Show,IssLoR\rbrace$, $\mathcal{O}_{sig-anon} \gets
    \lbrace HI,CI,Obtain,Issue,ObtIss,Show,SigLoR\rbrace$. $\mathcal{O}_{forge}
    \gets \lbrace HI,CI,Obtain,ObtIss,Issue,Show\rbrace$. $IssLor$ corresponds
    to \OBTCHALb in \UAS, whereas $SigLor$ corresponds to \CHALb. Also, \OWNR
    and \ATTR tables are essentially as in \secref{ssec:model-uas}.
    $\ISR[\ipk]$, in this case, returns the identifier of the issuer with public
    key \ipk. With $D = (l,D')$ we mean that the first attribute in the revealed
    set $D$ is $l$, which denotes the level of the credential used for
    authentication.}
  \label{fig:model-dac}  
\end{figure}

\subsubsection{\CUASDAC Construction.} %
We next give a construction of a delegatable AC (DAC) scheme, in the shape of
a $(\fissue^{l,\dattrs},\feval^{l,\dattrs},\finsp^0)$-$\CUASGen^{usr-iss}$
restriction, where the $\finsp^0$ function is as defined in
\figref{fig:func-restrictions}, and the \fissue and \feval variants are as
defined next:

\begin{align}
  & \fissue^{l,\dattrs}(\cdot,\attrs,(\cid,\cattrs)) \coloneqq
    \pcreturn (\attrs_1 = l+1 \land \attrs \subseteq
    \cup_{i\in\dattrs} \cattrs_i) \nonumber
  & \feval^{l,\dattrs}(\cdot,(\cid,\attrs),\cdot) \coloneqq
    \pcreturn((\attrs_1,\lbrace\attrs_i\rbrace_{i\in\dattrs}),\ast)
    \label{eq:funcs-rac}
\end{align}

. In a DAC scheme, all users are (or may be) also issuers. We only
distinguish between top-level issuers, who have level $l=0$, and lower-level
issuers, who have level $l>0$. In our \CUASDAC scheme, we assume that the first
attribute (after the user's secret key) encodes the level of the credential.
That is, $\attrs_1=l$, for a credential of level $l$. In addition, all users
(i.e., with $l>0$) who want to delegate have to publicly list:

\begin{enumerate}
\item The level $l$ of the credential they delegate.
\item Their public key \ipk.
\item An \UAS signature proving knowledge of a credential of level $l$, and over
  the attributes that this level-$l$ issuer is delegating.
\item The \ipk of the parent issuer.
\item The $\fissue^{l,\dattrs}$ function they will require for delegating.
\item An $\feval^{l,\dattrs}$ function used to produce the signature at item 3.
\end{enumerate}

We assume that, from an \ipk, it is possible to find the corresponding issuer
(e.g., using the previously mentioned public list). The mentioned
$\fissue^{l,\dattrs}$ functions must follow the pattern in \figref{fig:func-restrictions}.
Namely, the issuance function checks that the first requested attribute equals
$l+1$, and that all requested attributes are a subset of the attribute set
\dattrs being delegated by the level-$l$ issuer. In addition, signature
evaluation functions $\feval^{l,\dattrs}$, also shown in \figref{fig:func-restrictions},
must reveal the level of the credential used to produce the \UAS signature at
item 2, as well as the set of attributes \dattrs that the level-$l$ issuer
delegates. Verifiers can then trivially check if the set of revealed attributes
are contained within the attributes delegatable by the parent issuer%
\footnote{Additional checks may be added in both functions, but this is
  the bare minimum.}.
%
From this high-level description, we define the algorithms of \CUASDAC:

\begin{description}
\item[$\parm \gets \Setup(1^\secpar)$.]  Runs $\parm' \gets \Setup(1^\secpar)$
  and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our
  $\CUASGen^{usr-iss}$ construction. Returns $\parm \gets (\parm',\opk)$. Note
  that $\finsp^0$ can be replaced by any desired opening function.
\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] If $l=0$, simply run \IKeyGen as
  in $\CUASGen^{usr-iss}$. If $l>0$, this level-$l$ issuer picks a random
  message $r$ and computes $\Sig = (\sig,\yeval) \gets \Sign(\usk,\opk,\cred,r,
  \feval^{l,\dattrs})$, for the \dattrs set it wants to reveal -- which must
  include the attributes to delegate, and the credential level. It then
  publishes $(l,\ipk,\Sig,\ipk^{l-1},\fissue^{l,\dattrs},\feval^{l,\dattrs})$,
  where $\ipk^{l-1}$ is the public key of the parent issuer,
  $\fissue^{l,\dattrs}$ is an issuance function as described in
  \figref{fig:func-restrictions}, and $\feval^{l,\dattrs}$ is also as in
  \figref{fig:func-restrictions}, revealing the attributes that the issuer is
  willing to delegate.
% \item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] All users in this scheme are
%   also issuers. Thus, a new user runs first \IKeyGen as in \CUASGen. Then, sets
%   $\usk \gets \isk$ and stores \ipk, which may be needed to delegate obtained
%   credentials. Note that this does not affect security, as long as
%   $\isk \getr \AttrSpace$.
\item[$\langle \cred/\bot,\top/\bot \rangle \gets
  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
  If $l>0$, the user first finds the corresponding $(l,\ipk,\Sig,\ipk^{n-1},
  \fissue^{l,\dattrs},\feval^{l,\dattrs})$ tuple, and checks \Sig running
  \Verify as in $\CUASGen^{usr-iss}$ (with the retrieved $\feval^{l,\dattrs}$).
  Then, user and level-$l$ issuer run $\langle\Obtain,\Issue\rangle$ as in
  $\CUASGen^{usr-iss}$, using $\fissue^{l,\dattrs}$ as issuance function. If
  $l=0$, then both run $\langle\Obtain,\Issue\rangle$ as in
  $\CUASGen^{usr-iss}$, using the \fissue function required by the issuer.
\item[$\langle 1/0,(1,\utrans)/(0,\utrans)\rangle
  \gets \langle Show(\opk,\attrs,\dattrs,\cred),
  \Verify(\opk,\dattrs) \rangle$.] As in the interactive variant of
  $\CUASGen^{usr-iss}$.  
\end{description}

\paragraph{Security of \CUASDAC.} % 
We prove that \CUASDAC is an anonymous and unforgeable DAC scheme, according to
the model in \figref{fig:model-dac}, if the underlying \CUASGen construction has
anonymous issuance and signing, and has unforgeable issuance and signing.

\begin{theorem}[Issuance anonymity of \CUASDAC]
  If the base \CUASGen construction has issuance anonymity according to
  \defref{def:issue-anonymity-uas}, then \CUASDAC also has issuance anonymity.
\end{theorem}

\begin{proof}
  Given \adv~ against issuance anonymity of \CUASDAC as defined in
  $\Exp^{iss-anon-b}_{\adv,dac}(1^\secpar)$, we build an adversary \advB against
  issuance anonymity of \CUASGen as defined in \defref{def:issue-anonymity-uas}.

  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
  oracle, i.e.: for calls to $HU,CU,HI,CI,Obtain,Show,IssLoR$, \advB redirects
  to \HUGEN,\CUGEN,\IGEN,\ICORR,\OBTAIN,\SIGN,\OBTCHALb, respectively. Note that
  ``translating'' the inputs from the former into inputs for the latter is
  trivial. Obviously, if \adv~ wins in its issuance anonymity game, then so does
  \advB with the  same probability.
  % 
  \qed
\end{proof}

\begin{theorem}[Signature anonymity of \CUASDAC]
  If the base \CUASGen construction has signature anonymity according to
  \defref{def:sign-anonymity-uas}, then \CUASDAC also has signature anonymity.
\end{theorem}

\begin{proof}
  This is the same as in \thmref{thm:anon-cuasac}.
  % 
  \qed
\end{proof}

\begin{theorem}[Unforgeability of \CUASAC]
  If the base \CUASGen construction has issuance and signature unforgeability
  according to \defref{def:issue-forge-uas} and \defref{def:sign-forge-uas}, and
  non-frameability according to \defref{def:frame-uas}, then \CUASAC is an
  unforgeable AC scheme.
\end{theorem}

\begin{proof}
  First, we define the $ExtractChain(\utrans)$ function for our construction.
  Note that \utrans is a tuple $(r,\Sig)$\footnote{This follows for the approach
    to transform non-interactive signature and verification in \UAS to interactive
    presentations, as described in \secref{ssec:variants-gsac}.}, where $r$ is a
  fresh random number produced by the environment (acting as honest verifier),
  and \Sig is a \CUASGen signature over $r$. Thus, $ExtractChain$ leverages
  \ExtractSign from \CUASGen (see \secref{ssec:security-uas}) to get the
  credential and associated \ipk used to produce \Sig. Note that, for this
  \ipk, $\ipk = \ipk_{n-1}$ in $\Exp^{forge}_{\adv,dac}$. In \CUASDAC, we can
  leverage $\ipk_{n-1}$ to fetch from the public list a signature $\Sig_{n-1}$
  generated by the issuer owner of $\ipk_{n-1}$. Again, we apply \ExtractSign
  from \CUASGen, to get the credential one layer up in the chain.
  $ExtractChain$ repeats this step, until reaching the top level credential,
  issued by $\ipk_0$.

  For the proof, we first replace within $Setup$ the $\NIZKSetup$ algorithms for
  issuance and signing with their corresponding $\NIZKSetup$. Due to their
  zero-knowledge property, the resulting game is indistinguishable. Also, note
  that $ExtractChain$ succeeds to extract the corresponding credential chain,
  due to simulation extractability of the NIZKs.

  From the previous, the same reasoning as in \thmref{thm:forge-cuasac} applies
  to an adversary \adv~winning at line 5 of $\Exp^{forge}_{\adv,dac}$. Next,
  suppose that, from \utrans obtained at line 6, $ExtractChain$ outputs a
  delegation chain that makes \adv~win at line 10. This means that an
  uncorrupted issuer at position $i-1$ of the chain did not own a credential
  containing $D'$, but the issuer at position $i$ does. Then, either of the
  following must happen:

  \begin{itemize}
  \item The credential of the issuer at position $i$ is a forgery, meaning that
    it is a valid signature by the issuer at position $i-1$, who did not produce
    it. This can be used to break signature non-frameability of \CUASGen.
  \item The credential of the issuer at position $i$ is not a forgery, meaning
    that it is a valid signature by the issuer at position $i-1$, who produced
    it. But this contradicts the conditions required by $\fissue^{n,\dattrs}$,
    and therefore breaks issuance unforgeability of \CUASGen.
  \end{itemize}
  %
  \qed
\end{proof}

### 2022-07-28 prism-backend/research/gsac/app-related-proofs.tex
Moved RAC to main body, and DAC to app. Sync'ed RAC with new syntax.

\subsection{Security of \CUASDAC}

We prove that \CUASDAC is an anonymous and unforgeable DAC scheme, according to
the model in \figref{fig:model-dac}, if the underlying \CUASGen construction has
anonymous issuance and signing, and has unforgeable issuance and signing.

\begin{theorem}[Issuance anonymity of \CUASDAC]
  If the base \CUASGen construction has issuance anonymity according to
  \defref{def:issue-anonymity-uas}, then \CUASDAC also has issuance anonymity.
\end{theorem}

\begin{proof}
  Given \adv~ against issuance anonymity of \CUASDAC as defined in
  $\Exp^{iss-anon-b}_{\adv,dac}(1^\secpar)$, we build an adversary \advB against
  issuance anonymity of \CUASGen as defined in \defref{def:issue-anonymity-uas}.

  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
  oracle, i.e.: for calls to $HU,CU,HI,CI,Obtain,Show,IssLoR$, \advB redirects
  to \HUGEN,\CUGEN,\IGEN,\ICORR,\OBTAIN,\SIGN,\OBTCHALb, respectively. Note that
  ``translating'' the inputs from the former into inputs for the latter is
  trivial. Obviously, if \adv~ wins in its issuance anonymity game, then so does
  \advB with the  same probability.
  % 
  \qed
\end{proof}

\begin{theorem}[Signature anonymity of \CUASDAC]
  If the base \CUASGen construction has signature anonymity according to
  \defref{def:sign-anonymity-uas}, then \CUASDAC also has signature anonymity.
\end{theorem}

\begin{proof}
  This is the same as in \thmref{thm:anon-cuasac}.
  % 
  \qed
\end{proof}

\begin{theorem}[Unforgeability of \CUASAC]
  If the base \CUASGen construction has issuance and signature unforgeability
  according to \defref{def:issue-forge-uas} and \defref{def:sign-forge-uas}, and
  non-frameability according to \defref{def:frame-uas}, then \CUASAC is an
  unforgeable AC scheme.
\end{theorem}

\begin{proof}
  First, we define the $ExtractChain(\utrans)$ function for our construction.
  Note that \utrans is a tuple $(r,\Sig)$\footnote{This follows for the approach
    to transform non-interactive signature and verification in \UAS to interactive
    presentations, as described in \secref{ssec:variants-gsac}.}, where $r$ is a
  fresh random number produced by the environment (acting as honest verifier),
  and \Sig is a \CUASGen signature over $r$. Thus, $ExtractChain$ leverages
  \ExtractSign from \CUASGen (see \secref{ssec:security-uas}) to get the
  credential and associated \ipk used to produce \Sig. Note that, for this
  \ipk, $\ipk = \ipk_{n-1}$ in $\Exp^{forge}_{\adv,dac}$. In \CUASDAC, we can
  leverage $\ipk_{n-1}$ to fetch from the public list a signature $\Sig_{n-1}$
  generated by the issuer owner of $\ipk_{n-1}$. Again, we apply \ExtractSign
  from \CUASGen, to get the credential one layer up in the chain.
  $ExtractChain$ repeats this step, until reaching the top level credential,
  issued by $\ipk_0$.

  For the proof, we first replace within $Setup$ the $\NIZKSetup$ algorithms for
  issuance and signing with their corresponding $\NIZKSetup$. Due to their
  zero-knowledge property, the resulting game is indistinguishable. Also, note
  that $ExtractChain$ succeeds to extract the corresponding credential chain,
  due to simulation extractability of the NIZKs.

  From the previous, the same reasoning as in \thmref{thm:forge-cuasac} applies
  to an adversary \adv~winning at line 5 of $\Exp^{forge}_{\adv,dac}$. Next,
  suppose that, from \utrans obtained at line 6, $ExtractChain$ outputs a
  delegation chain that makes \adv~win at line 10. This means that an
  uncorrupted issuer at position $i-1$ of the chain did not own a credential
  containing $D'$, but the issuer at position $i$ does. Then, either of the
  following must happen:

  \begin{itemize}
  \item The credential of the issuer at position $i$ is a forgery, meaning that
    it is a valid signature by the issuer at position $i-1$, who did not produce
    it. This can be used to break signature non-frameability of \CUASGen.
  \item The credential of the issuer at position $i$ is not a forgery, meaning
    that it is a valid signature by the issuer at position $i-1$, who produced
    it. But this contradicts the conditions required by $\fissue^{n,\dattrs}$,
    and therefore breaks issuance unforgeability of \CUASGen.
  \end{itemize}
  %
  \qed
\end{proof}

>>>>

\subsection{Security of \CUASRAC}

We prove that \CUASRAC is an anonymous and unforgeable anonymous credential
scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
is anonymous and has unforgeable signing. Note that issuance unforgeability
of \CUASGen is not needed, as the model in \cite{fhs19} does not allow
leveraging other credentials not any fixed custom issuance policy. Thus,
signature unforgeability from \UAS is enough. Note that AC schemes modelled
as in \cite{fhs19} do not have issuance anonymity, as the user public key
is passed to the issuer.

\begin{theorem}[Anonymity of \CUASRAC]
  \label{thm:anon-cuasac}
  If the base \CUASGen construction has signature anonymity according to
  \defref{def:sign-anonymity-uas}, and $F$ is one-way and collision-resistant,
  then \CUASAC is an anonymous AC scheme according to \cite{fhs19}.
\end{theorem}

\begin{proof}
  Given \adv~ against anonymity of \CUASRAC as defined in
  \figref{fig:model-rac}, we build an adversary \advB against anonymity of
  \CUASGen as defined in \defref{def:sign-anonymity-uas}.

  First observe that, given a revocation handle $F(V,id)$ extracted from any
  credential showing, it is not possible to extract $id$, as $F$ is one-way
  and collision-resistant.

  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
  oracle, i.e.: for calls to $HU,CU,Obtain,Show,LoR,ReqCredHandle$, \advB
  redirects to \HUGEN, \CUGEN, \OBTAIN, \SIGN, \CHALb, of \OPEN respectively.
  Note that ``translating'' the inputs from the former into inputs for the
  latter is trivial. Also, observe that $ReqCredHandle$ essentially refuses to
  open transcripts from challenge users (signatures, in the non-interactive
  equivalent), as $F(V,\attrs_1(\ccid_0) \neq F(V,\attrs_1(\ccid_1)$ with
  overwhelming probability (see the $\tyinsp \neq \yinsp$) check in
  \figref{fig:oracles2}. Obviously, if \adv~ wins in its anonymity game, then
  so does \advB with the same probability.
  % 
  \qed
\end{proof}

\begin{theorem}[Unforgeability of \CUASRAC]
  If the base \CUASGen construction has sign unforgeability according to
  \defref{def:sign-forge-uas}, and $F$ is one-way and collision-resistant, then
  \CUASRAC is an unforgeable RAC scheme.
\end{theorem}

\begin{proof}
  Given \adv~ against unforgeability of \CUASRAC as defined in
  \figref{fig:model-rac}, we build an adversary \advB against sign
  unforgeability of \CUASGen as defined in \defref{def:sign-forge-uas}.

  To simulate oracle calls by \adv, \advB acts as in the anonymity proof. Assume
  that \adv~ wins its game via the winning condition of line 6 in the RAC
  unforgeability game. The same reasoning as in \CUASAC applies here. Next, note
  that the probability of \adv~ winning its game via the winning condition at
  line 9 is negligible, due to soundness of the NIZK scheme used for signing,
  and the one-wayness and collision-resistance of $F$ in
  $\feval^{\dattrs,F,V,L}$ and $\finsp^{F}$.
  % 
  \qed
\end{proof}
